Ants-Review: a Privacy-Oriented Protocol for Incentivized Open Peer-Reviews on Ethereum

### 2021-02-15 article.tex
Changes for Springer

\title{Ants-Review: an Ethereum-Based Protocol for Incentivized Peer Reviews}

@@

\email{bianca.trovo@alumni.unitn.it}\\

@@

\subsubsection{Supplementary Material}
Source code, DOI: 10.5281/zenodo.3971044;DApp: https://ants-review.on.fleek.co.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris and the four external anonymous peer reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}

>>>>

\title{Ants-Review: a Privacy-Oriented Protocol for Incentivized Open Peer-Reviews on Ethereum}

@@

\email{bianca.trovo@protonmail.com}\\

@@

\subsubsection{Supplementary Material}
Source code, DOI: 10.5281/zenodo.3971044; \\DApp: https://ants-review.on.fleek.co.

@@

\subsubsection{Acknowledgements} We would like to thank Andy Tudhope, Mark Beylin, Matteo A. Tambussi, Evan C. Harris and the four external anonymous peer reviewers for useful comments and revisions; the FDAPP 2020 workshop chairs and speakers for questions and feedback; Mitrasish Mukherjee for contributions on the interface.}
